<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-12-14 Working Rmds/MainAnalysis.Rmd
Add folder for working Rmds. Add Rmd to pull CvT data from database. Add updated MainAnalysis.Rmd file to use newly pulled CvT data.

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("invivopkfit")
# Clear memory:
rm(list=ls())
```

@@

```{r, load_cvt, eval = TRUE}
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
```

A couple of compounds had no CAS in CvTdb. Upon double checking, they should not have been added. So remove them. (CLR 2022-11-15: it doesn't look like there are any of these)

```{r, cvt_remove_nocas}
cvt.data <- cvt.data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")
```

Fix a few compound names.
```{r, cvt_fix_cpd_names}
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
```

if fk_reference_document is NULL, make fk_reference_document equal fk_extraction document. (CLR 2022-11-15: it doesn't look like there are any of these)

```{r}
cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
```

```{r}
### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")
```

Calculate a limit of quantification (90% of lowest observation)

```{r, calc_loq, eval = TRUE}
cvt.data <- estimate_loq(cvt.data)
```

Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm_ss.

@@

run_timestamp_1comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    run_timestamp_1comp,
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

run_timestamp_2comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    run_timestamp_2comp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat}
run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

@@

write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
                                    run_timestamp_flat,
                                    ".csv",
                                    sep=""), row.names = FALSE)
```

>>>>

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("../invivopkfit")
```

@@

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2022_12_13_17_09_45.csv")
```

Add LOQ when available.

PMIDs of documents

```{r}
unique(cvt_data[is.na(conc_time_values.conc),
                .(documents_extraction.pmid,
                  documents_extraction.doi,
                  documents_extraction.other_study_identifier,
                  documents_extraction.url)])
```

For PMID = 1233222, the original document has the LOQ as 0.08 ug/mL.

```{r}
cvt_data[documents_extraction.pmid %In% "1233222",
         c("loq_original",
                                                     "loq_original_units")= .(0.08,
                                                                              "ug/mL")]
```

Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm.

```{r}
timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M")
```

@@

@@

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    timestamp,
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

@@

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat}

@@

write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
                                    timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)
```
